\PassOptionsToPackage{svgnames}{xcolor}
\documentclass[11pt]{beamer}
%\usetheme{Singapore}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage[skins]{tcolorbox}
\newcommand{\cmark}{\textcolor{green}{\ding{51}}}%
\newcommand{\xmark}{\textcolor{red}{\ding{55}}}%

\newtcbox{\instbox}{enhanced,nobeforeafter,tcbox raise base,boxrule=0.2pt,top=0mm,bottom=0mm,
  right=0mm,left=0mm,arc=1pt,boxsep=1pt,before upper={\vphantom{dlg}}, frame hidden,
  colback=gray!25!white}

\MakeRobust\instbox 

\newtcbox{\regbox}{enhanced,nobeforeafter,tcbox raise base,boxrule=0.2pt,top=0mm,bottom=0mm,
  right=0mm,left=0mm,arc=1pt,boxsep=1pt,before upper={\vphantom{dlg}}, frame hidden,
  colback=Moccasin!75!white}

\MakeRobust\regbox
 
\newcommand{\acr}{reg.ac}
\newcommand{\inst}[1]{\instbox{\texttt{#1}}} % to display instructions
\newcommand{\reg}[1]{\regbox{\texttt{#1}}} % to register names or related 
%\author{}
%\title{}
%\setbeamercovered{transparent} 
\setbeamertemplate{navigation symbols}{} 
%\logo{} 
%\institute{} 
%\date{} 
%\subject{} 
\begin{document}

\section*{Microarchitecture Side-Channel Resistant Instructions Spans (scrispans)}
\frame{\sectionpage}

\begin{frame}{Examples semantics}
 
        \begin{itemize}
                \item \texttt{spansec.create [policies]}: create a new scrispan with given optional set of security policies (flags).
                \item \texttt{spansec.save rd}: save the current scrispan configuration (ID + security policy) in a register.
                \item \texttt{spansec.restore rs1}: restore a scrispan configuration from a register holding ID and security policy.
        \end{itemize}
                \textbf{We assume that a change of scrispan ID implies microarchitectural isolation.}
        \begin{itemize}
                \item \texttt{spansec.alter [policies]}: in addition we could add an instruction that keeps the ID unchanged but modify the security policies.
        \end{itemize}


\end{frame}

\begin{frame}{Proposed encoding 1}
    \begin{block}{}
        Using a custom opcode for now.
        The scrispan state is split between an ID (e.g. 24 bits) and policy flags (e.g. 8 bits).

        \begin{itemize}
            \item \inst{spansec.restore \reg{rs1}, \reg{imm}}: load ID and policy flags from \reg{rs1}, then update policies from \reg{imm}.
            \item \inst{spansec.save \reg{rd}}: store ID and policies in \reg{rd}.
        \end{itemize}

        Pseudo instructions:
        \begin{itemize}
            \item \inst{spansec.create \reg{imm}} = \inst{spansec.restore \reg{x0}, \reg{imm}}.
            \item \inst{spansec.alter \reg{imm}} = \inst{spansec.save \reg{xX}}; \inst{spansec.load \reg{xX}, \reg{imm}}.
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Proposed encoding 2}
    Using CSRs to store ID and policy flags.
    \begin{itemize}
        \item scrispan ID CSR = 0xXXX
        \item scrispan policies CSR = 0xYYY
    \end{itemize}

    Pseudo instructions:
    \begin{itemize}
        \item \inst{spansec.create \reg{imm}} = \inst{CSRRW \reg{x0}, \reg{x0}, 0xXXX}; \inst{CSRRI \reg{x0}, \reg{imm}, 0xYYY}
        \item \inst{spansec.save \reg{rd}} = \inst{CSRRW \reg{rd}, \reg{?}, 0xXXX}; + same for flags
    \end{itemize}
    Allow altering policies with \inst{CSRRS} and \inst{CSRRC}.
    Atomic behaviour of \inst{CSRRW} could be a good thing ?

\end{frame}


\end{document}